\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}
% Source - https://tex.stackexchange.com/a
% Posted by Pieter, modified by community. See post 'Timeline' for change history
% Retrieved 2026-01-23, License - CC BY-SA 3.0

% Adjust the page margins
\usepackage[scale=0.75]{geometry}

\usepackage{graphicx}
\usepackage{amsmath}

\usepackage{xcolor}
\definecolor{linkblue}{RGB}{0,70,140}
\usepackage{xparse}

\usepackage[
  colorlinks=true,
  linkcolor=linkblue,
  urlcolor=linkblue
]{hyperref}


\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}
\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}
\newcommand{\techstack}[1]{%
  \par\vspace{1pt}
  {\footnotesize\color{gray}\textbf{Tech Stack:} \textit{#1}}%
}

% Personal data
\name{Philipp}{Zettl}
\title{Backend Engineer \& Solutions Architect} 
\address{Berlin, Germany}{}{} 
\email{philipp@godesteem.de}
\social[github]{philsupertramp} 
\extrainfo{HuggingFace: \httpslink{hf.co/philipp-zettl}}

%----------------------------------------------------------------------------------
%            Content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle
\section{Professional Summary}
\cvitem{}{%
Result oriented Backend Engineer with 4+ experience designing, developing and
deploying scalable web backends using Python, FastAPI/Django and (non) relational or vector database systems.
Skilled in SDLC from requirement gathering to automated testing and experise in technical leadership, mentoring junior developers,
and driving engineering best practices.
Successfully architected a message processing system that parses and routes messages in parallel within $\approx 1.1$ seconds.
Passionate about writing open, clean, maintainable code and optimizing system performance.
}

\section{Skills}
\cvdoubleitem{\textbf{Languages}}{Python, Bash, C/\CC, MATLAB, Go, JavaScript}{\textbf{Frameworks \& ML}}{FastAPI, Django, Flask, PyTorch, Transformers, llama.cpp}
\cvdoubleitem{\textbf{Cloud \& DevOps}}{AWS, Docker, Kubernetes, Terraform, Terragrunt, Helm}{\textbf{Databases}}{MongoDB, Redis, SQLite, MySQL, PostgreSQL, Qdrant}

\section{Experience}

% Usage: \cventry{Year--Year}{Job Title}{Employer}{City}{}{Description}

\cventry{Jan 2025--Dec 2025}{Solutions Architect \& Founding Engineer}{easybits GmbH}{Berlin}{}{%
  \techstack{Python, Django, PostgreSQL, MongoDB, Qdrant, RabbitMQ, Docker, Kubernetes, Terraform, AWS, PyTorch, Transformers, sentence-transformers, llama.cpp}
\begin{itemize}
  \item Moved Python side of project from prototype state to production-grade services.
  \item Designed and implemented new automation solutions using self hosted models as well as API providers, e.g. semantic-search, text extraction for documents, text classification and image generation solutions.
  \item Introduced platform security mechanics, e.g. RFC like workflow for core changes, semantic versioning, release processes.
  \item Built up test case coverage for all ($\approx$ 10) Python projects to $\gte98\%$ and maintained the platform infrastructure on AWS (EKS cluster).
\end{itemize}}

\cventry{May 2022--Dec 2024}{Solutions Architect \& Lead Python Engineer}{MoBerries GmbH}{Berlin}{}{%
  \techstack{Python, Django, JavaScript, React, PostgreSQL, MongoDB, Qdrant, RabbitMQ, Docker, Kubernetes, Terraform, AWS, PyTorch, Tensorflow (2.0), Transformers, sentence-transformers}
\begin{itemize}
  \item Supervised Python team, architected solutions for platform and developed matching related features.
  \item Built in-house matching for the arabic language.
  \item Ran big scale evaluation of the matching algorithm for foreign governments during due diligence processes.
  \item Due to financial down sizing there was no team to supervise anymore after September 2024.
  \item Starting development of an asynchronous messaging platform for AI automation, which spun-off the easybits GmbH in 2025.
\end{itemize}}

\cventry{Oct 2018--Apr 2022}{Working Student Python Backend Engineering (20h/week)}{MoBerries GmbH}{Berlin}{}{%
  \techstack{Python, Django, JavaScript, React, PostgreSQL, MongoDB, RabbitMQ, Docker, Kubernetes, Terraform, AWS}
\begin{itemize}
  \item Developed features for the internal backend. Improved test code coverage and maintained the project in a team of 3 developers.
  \item Starting 2020 due to down sizing I took over the lead of all Python projects, including some tasks for the matching algorithm.
  \item In 2021 supervised small team of one full time and one part time developer.
  \item At the end of 2021 I took over the Machine Learning part of the company and developed several features for the candidate-job matching algorithm.
  This team grew until 2022 to three full time developers.
\end{itemize}}

\cventry{Oct 2017--Aug 2018}{Working Student Software Development}{PrintPeter GmbH}{Berlin}{}{%
  \techstack{Python, Django, PostgreSQL, MySQL, SQLite, HTML, CSS}\\
Supported C-level, marketing and product teams with SQL queries, full-stack development and template automation.}

\section{Selected Projects}
\cvitem{Factory}{REST API service for orchestrating GenAI tasks (Text, Image, Audio). \newline \href{https://github.com/philsupertramp/factory}{philsupertramp/factory}}
\cvitem{Label Ling}{Training recipes for producing production-grade NER models. \newline \href{https://github.com/philsupertramp/label-ling}{philsupertramp/label-ling}}
\cvitem{Chain Smoker}{Testing tool with a Go-based proxy to record and replay HTTP requests. \newline \href{https://github.com/philsupertramp/chain-smoker}{philsupertramp/chain-smoker}}
%\cvitem{Math Libs}{C++ libraries for game dev (`game-math`) and numerical data science (`ds.cpp`). \newline \href{https://github.com/philsupertramp/game-math}{philsupertramp/game-math}, \href{https://github.com/philsupertramp/ds.cpp}{philsupertramp/ds.cpp}}
%\cvitem{Docker Course}{Educational 3-day course covering Docker basics for developers. \newline \href{https://github.com/philsupertramp/docker}{philsupertramp/docker}}
%\cvitem{HuggingFace}{Active contributor of models and datasets for NLP and Multi-Modal tasks.}
}
\section{Teaching Experience}
\cventry{Summer 2023}{Lecturer}{Berliner Hochschule für Technik}{Berlin}{}{%
Taught "Introduction to Machine Learning" for the Embedded Systems studies.}

\section{Education}
\cventry{Graduated 2022}{B.Sc. in Mathematics}{Berliner Hochschule für Technik}{Berlin}{}{
\begin{itemize}
  \item \textbf{\href{https://github.com/philsupertramp/inet}{Thesis}}: "Machine Learning Methods for Localization and Classification of Insects in Images" (part of the \href{https://kinsecta.org}{KInsecta} research project).
  \item \textbf{Focus}: Applied Mathematics and Statistics.
  \item \textbf{Relevance}: Applied deep learning techniques for object detection on biological datasets, bridging theoretical math with practical ML implementation.
\end{itemize}}

\end{document}
